%%=============================================================================
%% Voorwoord
%%=============================================================================

\chapter*{\IfLanguageName{dutch}{Woord vooraf}{Preface}}
\label{ch:voorwoord}

%% TODO:
%% Het voorwoord is het enige deel van de bachelorproef waar je vanuit je
%% eigen standpunt (``ik-vorm'') mag schrijven. Je kan hier bv. motiveren
%% waarom jij het onderwerp wil bespreken.
%% Vergeet ook niet te bedanken wie je geholpen/gesteund/... heeft

Before you lies the bachelor's thesis “The headless usage of a traditional CMS to distribute centralised data". It has been written to fulfill the graduation requirements of the Applied Computer Science program at HogeSchool Gent (HoGent), with the specialization Mobile and Enterprise Developer.

As I am extremely interested in Content Management System as well as JavaScript frameworks, I wanted to do this research to extend my knowledge of these two subjects.

I want to thank my co-promotor Marek Tyczyński for always being available to give me feedback and answer my questions. Next to Marek, I could also count on the help of other employees of Dropsolid who are also excited about headless.

I also want to thank my promotor Lotte Van Steenberghe for giving me feedback about the structure of this thesis.

I want to thank my parents and my grandfather, who always supported and motivated me to keep going.

Finally I want to thank my girlfriend Emma, who is always by my side to support me.



